Proposed Solution

### 2016-11-14 Ennan-Proposal/intro.tex
autocommit

\section*{\app: Automated Verification of Configuration Files}
\paragraph{Overview:} 
Configuration errors (also known as misconfigurations) have become one of the major causes of system failures, resulting in security vulnerabilities, application outages, and incorrect program executions. 
Configuration errors were reported to be the largest fraction of failures in storage systems in a 2014 industry survey. 
Although many techniques have been proposed for configuration error detection, these approaches mainly can only be applied after an error has occurred.
Tools which detect misconfigurations at compile time often require the user to explicitly define constraints, a time consuming and error prone task.
We propose a framework to statically verify configuration files based on automatically generated constraints that define a correct file.
The core idea is to analyze many examples of configuration files from widely available datasets and derive a language model (a set of constraints) that can be used to verify new configuration files.

@@

\paragraph{Broader Impact:} 
Because configuration files are untyped, unstructured, and mostly undocumented, we are not directly leverage existing techniques for verification as used in programming languages.
Making progress towards verification in such environments, will open the door for work in other domain which have previously been to noisy to handle with existing techniques.
It would complement existing post-failure error diagnosis efforts, and could benefit other verification domains, such as network traffic verification. 
This could significantly reduce large scale system failures without adding any additional burden to users and system developers.

>>>>

\section*{\app: Automated Verification of Configuration Files}
\paragraph{Overview:} 
Configuration errors (also known as misconfigurations) have become one of the major causes of system failures, resulting in security vulnerabilities, application outages, and incorrect program executions. 
Configuration errors were reported to be the largest fraction of failures in a 2014 industry survey about storage systems. 
Although many techniques have been proposed for configuration error detection, most of these approaches can only be applied after an error has occurred.
Tools which detect misconfigurations at compile time often require the user to explicitly define constraints, a time consuming and error prone task.
We propose a framework to statically verify configuration files based on automatically generated constraints that define a correct file.
The core idea is to analyze many examples of configuration files from widely available datasets and derive a language model (a set of constraints) that can be used to verify new configuration files.

@@

\paragraph{Broader Impact:} 
Because configuration files are untyped and unstructured, our work represents a new direction that will complement existing techniques for verification as used in programming languages. 
Making progress towards verification in such environments, will enable work in other domains which have previously been to noisy to handle with existing techniques.
It would complement existing post-failure error diagnosis efforts, and could benefit other verification domains, such as network traffic verification. 
This could significantly reduce large scale system failures without adding any additional burden to users and system developers.
